---
title: "Mobility flows"
subtitle: "within four country groups based on their income level"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: spacelab
    source_code: embed
    fontsize: 16pt
---

```{r include = FALSE}
knitr::opts_chunk$set(echo=FALSE,warning=FALSE,message=FALSE)
```

```{r setup}
library(knitr)
library(htmltools)
library(dplyr)
library(manipulateWidget)

myfont="Times New Roman"
knitr::opts_chunk$set(echo = FALSE)

source("mobility_flow_income.R",local = knitr::knit_global())

data_long_income<-rbind(data_long_income_1,data_long_income_2,data_long_income_3)

# htmlwidgets::onRender(sankey1_income,
#   '
#   function(el,x) {
#     d3.select(el)
#       .selectAll(".node text")
#       .filter(function(d) { return d.name == "High"; })
#       .attr("x", x.options.nodeWidth - 16)
#       .attr("text-anchor", "end");
# 
#     d3
#       .selectAll("rect")
#       .filter(function (d, i) { return i === 5;})
#       .attr("width", x.options.nodeWidth * 2);
#   }
#   '
# )
sankey1 <- htmlwidgets::prependContent(sankey1_income)

sankey2 <- htmlwidgets::prependContent(sankey2_income)
sankey3 <- htmlwidgets::prependContent(sankey3_income)


combineWidgets(ncol=3,width=3*500,height=800,sankey1,sankey2,sankey3, myComment <- tags$div(
    class="text",
    tags$hr(),
    "early career stage"
  ),myComment <- tags$div(
    class="text",
    tags$hr(),
    "mid career stage"
  ),myComment <- tags$div(
    class="text", 
    tags$hr(),
    "late career stage"
  ))




```

```{css}

.text {
  height:100%;
  text-align: center;
}
```
This figure displays the movements within four groups of countries categorized based on their income level at three career stages. We counted the movements among all authors. The left/right side is related to the origin/destination country. The highest mobility flow happens between (and toward) high-income countries. At the later career stages, we observe increasing movements toward countries with lower income levels.

* H: High level, UM: Upper middle level, LM: Lower middle level, and L: Low level.